### 2014-03-29 ms_probaweb.tex
header
Update to the main text, with a reference to issue #4 on the main repo

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow,kpfonts}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes, backend=bibtex]{biblatex}
\usepackage{rotating}

@@

The occurrence of an interaction requires the co-occurrence of species $i$ and
$j$. This argument might seem trivial at first, but the explicit consideration
of this condition in the probabilistic representation of ecological networks
will prove fundamental to understand their variation.
% We already make this point in betalink, should we summarize it briefly?
We thus define $X_{iy}$
as a stochastic variable representing the occurrence of a species $i$ at
location $y$, and similarly $X_{ijy}$ the co-occurrence of species $i$ and
$j$. The quantity we seek to understand is the probability of a joint event:

%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy},)
\end{equation}
%-----------------

Which reads as the probability of observing species $i$, species $j$ and an
interaction between them. This probability could be further decomposed in two parts using the
product rule of probabilities:
%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy})=P(L_{ijy}|X_{iy},X_{jy},E_y)P(X_{iy},X_{jy}|E_y)
\end{equation}
%-----------------
We will refer to the left term as the metaweb. It is a conditional probability,
representing the probability that an interaction occurs if species $i$ and $j$
are co-occurring. The right term is the probability of observing the two species
co-occurring at location $y$.

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{color,lineno,setspace,multirow}
\usepackage[sc]{mathpazo}
\usepackage{graphicx}
\usepackage[top=2.4cm,left=2.4cm,top=2.4cm,bottom=2.4cm,includefoot]{geometry}
\usepackage[style=bes, backend=bibtex]{biblatex}
\usepackage{rotating}

@@

The occurrence of an interaction requires the co-occurrence of species $i$ and
$j$. This argument might seem trivial at first, but the explicit consideration
of this condition in the probabilistic representation of ecological networks
will prove fundamental to understand their variation.
% We already make this point in betalink, should we summarize it briefly?
We thus define $X_{i,y}$
as a stochastic variable representing the occurrence of a species $i$ at
location $y$, and similarly $X_{ij,y}$ the co-occurrence of species $i$ and
$j$. The quantity we seek to understand is the probability of a joint event:

%-----------------
\begin{equation}
   \text{P}(X_{i,y},X_{j,y},L_{ij,y},)
\end{equation}
%-----------------

Or simply said, the probability of observing both species $i$ and $j$, and
an interaction from $i$ to $j$. This probability could be further decomposed
in two parts using the product rule of probabilities:

%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy})=P(L_{ijy}|X_{iy},X_{jy},E_y)P(X_{iy},X_{jy}|E_y)
\end{equation}
%-----------------

We will refer to the left term as the metaweb. It is a conditional probability,
representing the probability that an interaction occurs if species $i$ and $j$
are co-occurring. The right term is the probability of observing the two species
co-occurring at location $y$.
